Title

### 2024-11-23 paper/paper.qmd
1. cross cite error fixed 2. minor mistake like typo fixed 3. paper re-render

The product pricing data for the "No Name" brand sold by Loblaws, used in this analysis, is included in the dataset provided by [@hammer]. This dataset compiles detailed product information, including vendors, product names, brands, categories, and unit prices. Additionally, it includes time-series pricing records for each product, capturing timestamps of price changes, current prices, unit prices, and quantities sold. These records are periodically updated on the Hammer platform to reflect the latest pricing trends. This dataset forms the foundation for analyzing price trends, identifying unit variations, and categorizing products into specific types for further analysis. Table @tbl-productdata previews the information for the target products included in this analysis, starting from June 2024.

@@

**Size**: Product size is a determinant of pricing, as larger sizes generally cost more due to the increased quantity. However, pricing strategies such as bulk discounts or price-per-unit variations can create non-linear relationships between size and price, making size an important factor to analyze.
**Type**: Product type (e.g., snacks, seasoning, dairy) reflects category-level differences in pricing strategies. Different types of products may have varying production costs, supply chain logistics, and market demand, all of which contribute to price fluctuations.
**Date**: Time plays an important role in grocery pricing due to reasons like seasonal demand, inflation, supply chain disruptions, and promotions. Analyzing the impact of time allows us to capture temporal trends and shifts in pricing behavior, such as rising costs during inflationary periods or discounts during specific seasons.

@@

The plot @fig-2 shows how average prices vary over time, segmented by product `type` (left) and `size` (right). In the left panel, we observe distinct pricing patterns across product types. For instance, "Seasoning" demonstrates higher volatility compared to "Flour/Rice," likely due to differences in demand elasticity. The "Milk" category shows occasional price dips, possibly influenced by the introduction of new products or promotional events.

@@

```{r, message=FALSE, fig.width=8, fig.height=3}
#| label: fig-1
#| fig-cap: Price Trend for Six of the Loblaws "No Name" Groceries Over Time (left) and Price Distribution by Size (right).
#| echo: false

@@

```{r, message=FALSE, fig.width= 7, fig.height= 3}
#| label: fig-2
#| fig-cap: Average Support Rate  for Donald Trump from 2024-07-21 to 2024-10-23 reported by different pollsters
#| echo: false
# Group data by date and product type, and calculate average price for each type per date
type_trend_data <- analysis_data %>%
  group_by(date, type) %>%
  summarise(avg_price = mean(current_price, na.rm = TRUE)) %>%
  ungroup()

@@

## Model justification
### Model Prior Selection, Assumptions, and Validation
Our prior selection was informed by the research in gamma modeling @Veazie2023GammaModel, we aim to provide sufficient flexibility for the model to adapt to the data. For example, the prior for the intercept was set as $\text{Normal}(2, 5)$, reflecting the assumption that the baseline log-transformed price of Loblaws "No Name" products fluctuates around 2 while allowing for some uncertainty. For the effect coefficients of variables such as size, type, and date, we chose priors of $\text{Normal}(0, 5)$, representing the expectation of moderate impacts of these variables on pricing. These priors enable the model to adjust based on observed data.

>>>>

The product pricing data for the "No Name" brand sold by Loblaws, used in this analysis, is included in the dataset provided by [@hammer]. This dataset compiles detailed product information, including vendors, product names, brands, categories, and unit prices. Additionally, it includes time-series pricing records for each product, capturing timestamps of price changes, current prices, unit prices, and quantities sold. These records are periodically updated on the Hammer platform to reflect the latest pricing trends. This dataset forms the foundation for analyzing price trends, identifying unit variations, and categorizing products into specific types for further analysis. @tbl-view previews the information for the target products included in this analysis, starting from June 2024.

@@

**Size**: Product size is a determinant of pricing, as larger sizes generally cost more due to the increased quantity. However, pricing strategies such as bulk discounts or price-per-unit variations can create non-linear relationships between size and price, making size an important factor to analyze.

**Type**: Product type (e.g., snacks, seasoning, dairy) reflects category-level differences in pricing strategies. Different types of products may have varying production costs, supply chain logistics, and market demand, all of which contribute to price fluctuations.

**Date**: Time plays an important role in grocery pricing due to reasons like seasonal demand, inflation, supply chain disruptions, and promotions. Analyzing the impact of time allows us to capture temporal trends and shifts in pricing behavior, such as rising costs during inflationary periods or discounts during specific seasons.

@@

@fig-2 shows how average prices vary over time, segmented by product `type` (left) and `size` (right). In the left panel, we observe distinct pricing patterns across product types. For instance, "Seasoning" demonstrates higher volatility compared to "Flour/Rice," likely due to differences in demand elasticity. The "Milk" category shows occasional price dips, possibly influenced by the introduction of new products or promotional events.

@@

```{r, message=FALSE, warning=FALSE, fig.width=8, fig.height=3}
#| label: fig-1
#| fig-cap: Price Trend for Six of the Loblaws "No Name" Groceries Over Time (left) and Price Distribution by Size (right).
#| echo: false

@@

```{r, message=FALSE, warning=FALSE, fig.width= 7, fig.height= 3}
#| label: fig-2
#| fig-cap: Average Support Rate  for Donald Trump from 2024-07-21 to 2024-10-23 reported by different pollsters
#| echo: false
# Group data by date and product type, and calculate average price for each type per date
type_trend_data <- analysis_data %>%
  group_by(date, type) %>%
  summarise(avg_price = mean(current_price, na.rm = TRUE)) %>%
  ungroup()

@@

## Model justification
### Model Prior Selection, Assumptions, and Validation
Our prior selection was informed by the research in gamma modeling @Veazie2023GammaModel, we aim to provide sufficient flexibility for the model to adapt to the data. For example, the prior for the intercept was set as $\text{Normal}(2, 5)$, reflecting the assumption that the baseline log-transformed price of Loblaws "No Name" products fluctuates around 2 while allowing for some uncertainty. For the effect coefficients of variables such as `size`, `type`, and `date`, we chose priors of $\text{Normal}(0, 5)$, representing the expectation of moderate impacts of these variables on pricing. These priors enable the model to adjust based on observed data.
